\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-02-17 doc/publications/plos16/supplementary_information.tex
added H2O times to sulementary info

\multirow{3}{*}{phase1\_chr22: 1,092 x 490,036} & \cursedforest\ & 0.077 (XX) &                  &                                                                   \\
                                                & RF - Spark ML  &            &                  &                                                                   \\
                                                & RF - R         & 0.05       & 24 min           & 18GB\footnote{using the \texttt{parallel} packages with 10 nodes} \\
                                                & ranger - R      & 0.06       & 1 min 10 seconds & 16GB  (one processor)                                             \\
                                                & ranger - c++     & 0.06       & 7 mins           & --nthreads 20                                                     \\

>>>>

\multirow{3}{*}{phase1\_chr22: 1,092 x 490,036} & \cursedforest\ & 0.077 (XX) &                  &                                                                   \\
                                                & RF - Spark ML  &            &                  &                                                                   \\
                                                & RF - R         & 0.05       & 24 min           & 18GB\footnote{using the \texttt{parallel} packages with 10 nodes} \\
                                                & ranger - R      & 0.06       & 1 min 10 seconds & 16GB  (one processor)                                             \\
                                                & ranger - c++     & 0.06       & 7 mins           & --nthreads 20                                                    \\
                                                & H2O           & 0.06       & 5 hours         & 600GB \footnote{java -Xmx600g -jar h2o.jar,   h2o.init(nthreads=20)} \\
